---
title: "ScoobyGrader_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ScoobyGrader_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
Welcome to package ScoobyGrader! This package is designed to help graders visualize the score distribution of a particular assignment, as well as make weighted grade calculations fast and simple. Scooby inspiration comes in the form of function ScoobyGrade(), where the user has the option to choose from all 5 crime fighters to choose a color palette for an assignment's grade distribution. As long as the user has a dataset following the format of the embedded dataset, user should be able to add/drop columns for calculating weighted grades and visualizing an individuals students progress.
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Load the package.
```{r setup}
library(ScoobyGrader)
```

To get started with this package let's take a look at our first function for calculating weighted grades after the semester, weighted_grade(). Enter your dataset with the first argument in the function. Each corresponding argument is to fill in which assignment you would like to add the calculation. Beware of the percent weight given to each assignment. You will be able to alter the weight and number of assignments within the function. 
```{r}
weighted_grade= function(data, exam1, exam2, final, lab, students, prbSet){
  subSec<- data[students, prbSet]
  
  meanie<- apply(subSec,1,FUN=mean)
  
  data$meanGrade<- meanie
  
  weighted<- ((data[[exam1]] * .2) + (data[[exam2]] * .2) + (data[[final]] * .3) + (data[[lab]] * .2) + (data$meanGrade * .1))
  data$weightedTotal<- weighted
  
  return(data)
}

```

Let's look at an example. *Note* that we are telling our function the rows of students to do the calculation for and which columns of problem sets to average for our overall calculation.
```{r}
weighted_grade(classScores, "Exam.1", "Exam.2", "Final.exam", "Lab", students=1:166, prbSet=7:18)
```
Next, let's look at our students progess function.
```{r}
semPro= function(data, student){
  
  Grade <- subset(data, data[["Student"]] == student)
  
  Grade <- unlist(Grade[,3:17])
  plot(Grade, type = "l", lty=2, xlab= "Assignment #", col='plum')
  return(plot)
}
```

We will insert the dataset being examined and the student whose progress we want to track. Make sure to copy the name exactly as it's written in the dataset.
```{r}
semPro(classScores, "Abreu, Jose")
```

Our final, and favorite!, function is ScoobyGrade(). This is a simple plotting function that shows the class distributiton of a single assignment using the color palette of a specific Scooby Doo character. Simply specify which dataset to use, the assignment you'd like to plot, and the color scheme of one character, shown below.
```{r}
ScoobyGrade= function(data, assignment, scoobCharac){
 
  if (scoobCharac=="Shaggy"){
    hist(data[ ,assignment],xlim= c(50,100), main= "Grade Distribution", xlab= "Grade", ylab= "# of Students", col=c("olivedrab","tomato4"), border= "black")
  } else if (scoobCharac=="Fred"){
    hist(data[ ,assignment],xlim= c(50,100), main= "Grade Distribution", xlab= "Grade", ylab= "# of Students", col=c("white", "deepskyblue3"), border= "orange2")
  } else if (scoobCharac=="Velma"){
    hist(data[ ,assignment],xlim= c(50,100), main= "Grade Distribution", xlab= "Grade", ylab= "# of Students", col="orange1", border= "firebrick3")
  } else if (scoobCharac=="Daphne"){
    hist(data[ ,assignment],xlim= c(50,100), main= "Grade Distribution", xlab= "Grade", ylab= "# of Students", col=c("plum4", "thistle"), border= "olivedrab2")
  } else if (scoobCharac=="Scooby"){
    hist(data[ ,assignment], xlim= c(50,100), main= "Grade Distribution", xlab= "Grade", ylab= "# of Students", col=c("tan3", "black"), border= "turquoise3")
  }
}
```

Let's look at the Scooby plot below.
```{r}
ScoobyGrade(classScores, "Final.exam", "Scooby")
```

As long as all headers and student names are spelled exactly, there should be no issues using this package. 